With Great Growth, Comes Greater Consumption: Energy consumption of countries around the world inb relation to their GDP growth

### 2024-04-22 paper/paper.qmd
paper titlee and subtitle

---
title: "With great growth, comes greater Consumption: Energy consumption of countries around the world"
subtitle: "An analysis of economic growth and Energy consumption globally"
author: 
  - Rayan Awad Alim
thanks: "Code and data are available at: https://github.com/RayanAlim/Energy-Analysis"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "With Great Growth, Comes Greater Consumption: Energy consumption of countries around the world inb relation to their GDP growth"
subtitle: "An analysis of economic growth and Energy consumption globally between 1992 to 2022"
author: 
  - Rayan Awad Alim
thanks: "Code and data are available at: https://github.com/RayanAlim/Energy-Analysis"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
